Shallow EDSLs and Object-Oriented Programming

### 2016-06-30 paper/sections/Introduction.tex
Add references

\noindent Although the above definition is quite reasonable and widely accepted,
it leaves some space to (mis)interpretation. For example it is unclear 
how to classify an EDSL implemented using the {\sc Composite} or {\sc Interpreter} 
patterns in Object-Oriented Programming (OOP). Would this OO approach be
classified as a shallow or deep embedding? We feel there is a rather
fuzzy line here, and the literature allows for both interpretations. Some authors working on
OOP EDSLs ~\cite{} consider a {\sc Composite} to be a deep
embedding. Some other authors~\cite{gibbons2014folding} 
consider implementations using tuples and/or the  {\sc Composite}
pattern to be a shallow embedding.

>>>>

\noindent Although the above definition is quite reasonable and widely accepted,
it leaves some space to (mis)interpretation. For example it is unclear 
how to classify an EDSL implemented using the {\sc Composite} or {\sc Interpreter} 
patterns in Object-Oriented Programming (OOP). Would this OO approach be
classified as a shallow or deep embedding? We feel there is a rather
fuzzy line here, and the literature allows for both interpretations. Some authors working on
OOP EDSLs ~\cite{rompf2012scala,scherrc2015} consider a {\sc Composite} to be a deep
embedding. Some other authors~\cite{gibbons2014folding,barringer2011tracecontract}
consider implementations using tuples and/or the  {\sc Composite}
pattern to be a shallow embedding.
